### 2022-02-16 README.Rmd
ArXiv readme

[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf)

@@

Douglass, Rex W.,  Thomas Leo Scherer, J. Andrés Gannon, Erik Gartzke, Jon Lindsay, Shannon Carcelli, Jonathan Wiklenfeld, David M. Quinn, Catherine Aiken, Jose Miguel Cabezas Navarro, Neil Lund, Egle Murauskaite, and Diana Partridge. 2022. "Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises." Unpublished Manuscript. Retrieved from https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset.

>>>>

[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf).

The [ArXiv pre-print](https://arxiv.org/abs/2202.07081) was posted on February 15, 2022.

@@

Douglass, Rex W., Thomas Leo Scherer, J. Andrés Gannon, Erik Gartzke, Jon Lindsay, Shannon Carcelli, Jonathan Wiklenfeld, David M. Quinn, Catherine Aiken, Jose Miguel Cabezas Navarro, Neil Lund, Egle Murauskaite, and Diana Partridge. 2022. "Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises." arXiv:2202.07081 [cs, stat]. http://arxiv.org/abs/2202.07081.
